How many researchers use 'boilerplate' statistical analysis sections?

### 2021-03-16 manuscript/draft_manuscript.Rmd
Update draft_manuscript.Rmd

Many researchers lack adequate training in research methods, and statistics is something they do with trepidation and even ignorance [@Altman1994;@King2019]. 
However, using the wrong statistical methods can cause real harm [@Altman1994] and bad statistical practices are being to used abet weak science [@Stark2018].
Statistical mistakes are a key source of waste in research and partly explain the current reproducibility crisis in science [@Allison2016]. Even when the correct methods are used, many researchers fail to describe them adequately, making it difficult to reproduce the results [@Ernst2017;@Zhou2018].
Poor statistical methods might not be caught by reviewers, as they may not be qualified to judge the statistics.
A recent survey of editors found that only 23% of health and medical journals used expert statistical review for all articles [@Hardwicke2020], which was little different from a survey from 22 years ago [@Goodman1998].

>>>>

Many researchers lack adequate training in research methods, and statistics is something they do with trepidation and even ignorance [@Altman1994;@King2019]. 
However, using the wrong statistical methods can cause real harm [@Altman1994;@Brown2018] and bad statistical practices are being to used abet weak science [@Stark2018].
Statistical mistakes are a key source of waste in research and partly explain the current reproducibility crisis in science [@Allison2016]. Even when the correct methods are used, many researchers fail to describe them adequately, making it difficult to reproduce the results [@Ernst2017;@Zhou2018].
Poor statistical methods might not be caught by reviewers, as they may not be qualified to judge the statistics.
A recent survey of editors found that only 23% of health and medical journals used expert statistical review for all articles [@Hardwicke2020], which was little different from a survey from 22 years ago [@Goodman1998].
